% Modified from the template below
% Secondary author: Dylan Paddock (dylan.paddock@gmail.com)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\definecolor{color1}{RGB}{40, 65, 120} % Adjust coloring to a deeper blue

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvicons{awesome}

\usepackage[margin=2.1cm,top=2.1cm,bottom=2cm]{geometry} % Reduce document margins. Don't go below 1cm for printing.

\usepackage{tgheros}
\usepackage{xcolor}
\usepackage{xpatch}

\renewcommand{\familydefault}{\sfdefault}
\usepackage[T1]{fontenc}
\newcommand{\vs}[0]{\smallskip}

\renewcommand{\listitemsymbol}{--~} % Changes the symbol used for lists

\usepackage[notext,notextcomp]{stix}
\usepackage{newunicodechar}
\newunicodechar{〒}{\texttt{$\postalmark$}}

% Remove the arbitrary 80% width restriction for the name
\patchcmd{\makehead}
  {\setlength{\makeheaddetailswidth}{0.8\textwidth}}
  {\setlength{\makeheaddetailswidth}{\textwidth}}
  {\typeout{patch success}}
  {\typeout{patch failure}}

% Add additional whitespace between the name and address
\patchcmd{\makehead}
  {\addressfont\color{addresscolor}}
  {\vspace{0.1cm}\addressfont\color{addresscolor}}
  {\typeout{patch success}}
  {\typeout{patch failure}}


%----------------------------------------------------------------------------------------
% NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\usepackage{hyperref}

\name{}{DYLAN HIROSHI TAKAYASU PADDOCK}
\extrainfo{\faHome\>Kyoto, Japan}
\email{dylan.paddock@gmail.com}
\social[linkedin][www.linkedin.com/in/dylanpaddock]{dylanpaddock}
\social[github][github.com/dylan-mistplay]{dylan-mistplay}

% Generate the header and adjust vertical whitespace
\begin{document}
\makecvtitle % Print the CV title
\vspace{-0.9cm}


%----------------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY SECTION
%----------------------------------------------------------------------------------------
\section{Professional Summary}
\vspace{-0.8mm}
Highly-skilled Android engineer with 7\texttt{+} years experience and an international background. Founding engineer of Mistplay, a gaming adtech platform. Played a pivotal role in scaling the company from inception to 250+ employees, hundreds of millions of dollars in annual revenue, and successful acquisition. 

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

% Usage: \cventry{start time -- end time}{job title}{{employer}}{city}{}{responsibilities}\vs

% Mistplay Growth Stage
\cventry
{March 2022 -- January 2025}
{Senior Softwaree Engineer \& Tech Lead -- Android}
{{Mistplay}}
{New York, USA (Remote)}
{}{
	Delivered meticulously-crafted, robust, scalable solutions on ambitious timelines. Built beautiful, intuitive, animated UI.
	Led a cross-functional team of ten, collaborating closely with stakeholders.
	Architected and led the development of complex features, apps and SDKs, such as a modular rewrite of the retail platform used both in-app and as an SDK.
	Championed the adoption of Modern Android Development and Clean Architecture, accelerating feature development for the team and surpassing business goals. Notably, a side project to refactor the core monetization loop grew app revenue by 10\%. Also, worked with designers to build a custom design system to share components across all Mistplay projects, halving UI development time.
	Mentored and managed engineers to foster a highly-collaborative, multicultural engineering organization with an emphasis on continuous improvement, establishing best practices, and helping team members fulfill their potential.
}\vs

% Mistplay Startup
\cventry
{January 2018 -- March 2022}
{Fullstack Software Engineer}
{{Mistplay}}
{Montreal, Canada}
{}
{
	Delivered polished, maintainable, user-friendly features for native Android and Node.js in a fast-paced startup environment.
	Drove engineering innovation, leading the charge for the adoption of Modern Android, including Kotlin, MVVM, and Jetpack Compose.
	Managed weekly fullstack releases and feature experiments while maintaining 99.99\% service uptime and 99.9\% crash-free users, scaling the app infrastructure to meet the needs of the userbase as it grew 100-fold over two years.
	Worked closely with a rapidly growing agile organization, mentoring new hires and collaborating with external teams.
}\vs

%maple
\cventry{March 2016 -- July 2017}{Native English Instructor}{{Maple English School}}{Okayama, Japan}{}{Taught English, math and computer science to Japanese students. Developed teaching materials and trained new teachers.}\vs

%vienna
\cventry{June -- July 2012}{Research Intern}{{The Vienna University of Technology}}{Vienna, Austria}{}{Researched road traffic congestion and programmed models for use in model-predictive control systems.}

%----------------------------------------------------------------------------------------
%   SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
\vspace{-0.8mm}
\cvitem{Android Development}{Kotlin, Java, Android SDK, Clean Architecture, Jetpack Compose (including Compose Navigation, Animations, and Design Systems), MVVM, Dependency Injection (Koin, Dagger), Data Persistence (Room, Datastore), Networking (Retrofit, Ktor), Coroutines, Flow, Gradle}
\cvitem{App Development}{Analytics, Monitoring, Performance Optimization, Feature Flags \& AB Testing, Accessibility, Codebase Modularization, Localization, Internationalization, SDK Development, Documentation, Release Management, Git, GitHub, Security, Fraud Detection, Software Architecture, System Design, Authentication (JWT, OAuth, SSO), CI/CD Pipelines (Github Actions, CircleCI)}
\cvitem{Backend and Infrastructure}{Javascript, Typescript, Python, Node.js, Amazon Web Services (DynamoDB, EB, Elasticache, S3, EC2, CloudWatch, IAM), Docker, Kubernetes, Redis, REST API Design, Microservices}
\cvitem{Game Development}{Unity, C\#, OpenGL}
\cvitem{Collaboration}{Code Review, Mentorship, Agile Methodology, Collaboration Tools (including Jira, Asana, and Notion), Cross-Cultural Communication, Continuous Learning \& Improvement, Technical Leadership}
\cvitem{Language}{Native English, Advanced Spanish, Conversational Japanese}


%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{Jan 2011 -- May 2015}{UC Berkeley College of Engineering}{B.Sc. in Electrical Engineering and Computer Science}{Berkeley, USA}{}{
\cvlistitem{GPA 3.718; Dean's Honor List (all semesters)}
\cvlistitem{Eta Kappa Nu Electrical and Computer Engineering Honor Society (2013)}
\cvlistitem{Tau Beta Pi Engineering Honor Society (2012)}
}

\end{document}